Massively Parallel Monte Carlo Methods for Linear and Nonlinear Problems

### 2012-10-02 doc/prelim/presentation/prelim_presentation.tex
adding Chimera linear problem container

%%---------------------------------------------------------------------------%%
\newcommand{\vA}{\ensuremath{\ve{A}}}
\newcommand{\vb}{\ensuremath{\ve{b}}}
\newcommand{\vx}{\ensuremath{\ve{x}}}
\newcommand{\vr}{\ensuremath{\ve{r}}}
\newcommand{\vu}{\ensuremath{\ve{u}}}
\newcommand{\vI}{\ensuremath{\ve{I}}}
\newcommand{\vH}{\ensuremath{\ve{H}}}
\newcommand{\vP}{\ensuremath{\ve{P}}}

\newcommand{\Cv}{\ensuremath{C_{v}}}
\newcommand{\ros}{\ensuremath{\sigma_{\scriptscriptstyle\mathrm{R}}}}
\newcommand{\bOmega}{\ensuremath{\mathbf{\Omega}}}

\newcommand{\dt}{\ensuremath{\Delta t}}
\newcommand{\sign}{\ensuremath{\tilde{\sigma}^n}}
\newcommand{\qn}{\ensuremath{q^n}} \newcommand{\Tn}{\ensuremath{T^n}}
\newcommand{\Dn}{\ensuremath{D^n}}
\newcommand{\phin}{\ensuremath{\phi^n}}
\newcommand{\Di}{\ensuremath{\Delta_i}}
\newcommand{\Dj}{\ensuremath{\Delta_j}}
\newcommand{\Dk}{\ensuremath{\Delta_k}}

\newcommand{\sigT}{\ensuremath{\sigma_{T\,ijk}}}
\newcommand{\sigm}{\ensuremath{\sigma^{-}}}
\newcommand{\sigp}{\ensuremath{\sigma^{+}}}

\newcommand{\bphi}{\ensuremath{\boldsymbol{\phi}}}

\DeclareMathOperator{\diag}{diag}
%%---------------------------------------------------------------------------%%

\author{Stuart R. Slattery
  \\ Engineering Physics Department
  \\ University of Wisconsin - Madison
  \\ \href{mailto:sslattery@wisc.edu}{\texttt{sslattery@wisc.edu}}
}

@@

%%---------------------------------------------------------------------------%%
\begin{frame}{Hardware-Based Motivation}
  \begin{itemize}
    \item
  \end{itemize}
\end{frame}

>>>>

%%---------------------------------------------------------------------------%%
\author{Stuart R. Slattery
  \\ Engineering Physics Department
  \\ University of Wisconsin - Madison
  \\ \href{mailto:sslattery@wisc.edu}{\texttt{sslattery@wisc.edu}}
}

@@

%%---------------------------------------------------------------------------%%
\begin{frame}{Hardware-Based Motivation}
  \begin{itemize}
    \item Modern hardware is moving in two directions: lightweight
      machines and heterogeneous machines characterized by low power
      and high concurrency.
    \item High concurrency and low cost units means a higher potential
      for both soft and hard failures.
    \item Monte Carlo methods bury soft failures within the variance
      of the tallies while hard failures are high variance events.
    \item New machines will also be memory restricted with a continued
      decrease of memory/FLOPS predicted.
    \item Compared to conventional methods, we will show that Monte
      Carlo methods offer a memory savings.
  \end{itemize}
\end{frame}
